---
title: "AirBnB - NYC"
author: "Amin Yakubu"
date: "10/9/2018"
output: github_document
---


```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

```{r}
library(tidyverse)
library(p8105.datasets)

data(nyc_airbnb)

```

```{r, eval = FALSE}
nyc_airbnb %>% View
```

```{r}
airbnb = nyc_airbnb %>% 
  mutate(starts = review_scores_location/2) %>% 
  rename(boro = neighbourhood_group)

airbnb %>% 
  count(boro, neighbourhood)
```


## Some questions

* Does rating vary by neighborhood, room type or both?
* How is pice related to other variables?
* Where are rentals located?
* What's the most expensive area? What about the least?
* Which listing have the most unfilled days? 
* Which area has the highest density of listings?
* What are some host characteristics? What's associated with ratings?

```{r}
airbnb %>% 
  select(neighbourhood, price) %>% 
  group_by(neighbourhood) %>% 
  summarize( number = n(),
             mean_price = mean(price, na.rm = FALSE),
             median_price = mean(price, na.rm = FALSE)) %>% 
  top_n(5, mean_price)

airbnb %>% 
  select(neighbourhood, price) %>% 
  group_by(neighbourhood) %>% 
  summarize( number = n(),
             mean_price = mean(price, na.rm = FALSE),
             median_price = mean(price, na.rm = FALSE)) %>% 
  top_n(-5, mean_price)
```

##### Where are rentals located?

```{r}
airbnb %>% 
  ggplot(aes(x = longitude, y = latitude, color = price)) +
  geom_point(alpha = .2) +
  facet_grid(~room_type) +
  scale_color_viridis_c()

```
